Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-03-08 writeup/gz_hubble_data.tex
updated hubble catalog with complete set of redshifts

\begin{table*}
\caption{Breakdown of what we can correct out of the GZH data, by sample.  \label{hubble_debiasable}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                  & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & GOODS FULL   & SDSS    & Total \\
\hline
Correctable                        & 1,628   & 15,120 & 1,811 & 739    & 502     & 1,850	& 0       & 21,650\\
Uncorrectable                      & 1,869   & 26,184 & 2,407 & 524    & 1,115   & 2,670	& 0       & 34,769\\
No Correction Needed ($z \le 0.3$) & 944     & 11,781 & 1,193 & 258    & 258     & 1,083	& 37,545  & 53,062\\ 
NEI                                & 2,753   & 34,432 & 2,271 & 861    & 2,547   & 4,766	& 0       & 47,630\\
No Redshift Information            & 1,313   & 5,291  & 1,622 & 169    & 491     & 788		& 14,316  & 23,990\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 11,157	& 51,861  & 181,101\\
\hline\hline
\end{tabular}
\end{table*}

@@

\end{document}

>>>>

\begin{table*}
\caption{Breakdown of what we can correct out of the GZH data, by sample.  \emph{updated from 3-8-16: Switching to full depth for all GOODS data. Shallow depth information in appendix.}\label{hubble_debiasable}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                  & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S         & SDSS    & Total \\
\hline
Correctable                        & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
Uncorrectable                      & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
No Correction Needed ($z \le 0.3$) & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
NEI                                & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
No Redshift Information            & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
Total                              & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
\hline\hline
\end{tabular}
\end{table*}

@@

\newpage
\clearpage
\appendix
\section{GOODS Shallow Depth data}

GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of images. The 11,157 full depth 5-epoch images are used in the main catalog; the classifications for the 7,464 shallow depth 2-epoch images are offered as a supplementary table. Here we briefly analyze the effect of image depth on the ability of the GZ users to identify features or disk structure in the images.

4,461 galaxies have both full depth and shallow depth classifications. 
\end{document}
